\section{Graphs}

\subsection{Topological sort}

\underline{Runtime:} $\mathcal{O}(\lvert V \rvert + \lvert E \rvert)$
\lst{Kahn}{graphs/topoSort.cc}

\subsection{Connected components}

\subsubsection{Bridges}

Bridges are edges that increase the number of connected components if
removed.

\underline{Runtime:} $\mathcal{O}(\lvert V \rvert + \lvert E \rvert)$
\lstwot{graphs/bridges.cc}

\subsubsection{Articulation Points}

Articulation Points are vertices that increase the number of connected
components if removed.

\underline{Runtime:} $\mathcal{O}(\lvert V \rvert + \lvert E \rvert)$
\lstwot{graphs/articulationPoints.cc}

\subsubsection{Strongly connected components}
\underline{Runtime:} $\mathcal{O}(\lvert V \rvert + \lvert E \rvert)$
\lst{SCC Tarjan}{graphs/scc.cc}


\subsection{Minimal spanning tree}
\underline{Runtime:} $\mathcal{O}(\lvert E \rvert \log \lvert V
\rvert) = \mathcal{O}(\lvert E \rvert \log \lvert E \rvert)$
\lst{Kruskal}{graphs/kruskal.cc}

\subsection{Shortest paths}

\subsubsection{Single source shortest path}
\underline{Runtime:}
$\mathcal{O}((\lvert E \rvert + \lvert V \rvert )\log \lvert V
\rvert)$
\lst{Djikstra}{graphs/djikstra.cc}

\underline{Runtime:} $\mathcal{O}(\lvert E \rvert \lvert V \rvert)$
\lst{Bellman Ford}{graphs/bellmanFord.cc}

This approach may be faster
\lst{Bellman Ford w/ Queue}{graphs/bellmanFordQueue.cc}
\subsubsection{All pairs shortest paths}
\underline{Runtime:} $\mathcal{O}(\lvert V \rvert^3)$
\lst{Floyd Warshall}{graphs/floydWarshall.cc}

\subsubsection{Lowest common ancestor}
\underline{Runtime:} build: $\mathcal{O}(\lvert V \rvert \log \lvert
V\rvert)$ query: $\mathcal{O}(1)$
\lstwot{graphs/LCA.cc}

\underline{Runtime:} build: $\mathcal{O}(|V|\log |V|)$ query: $\mathcal{O}(\log|V|)$
\lst{LCA w/ binary lifting + max weighted edge on path}{graphs/LCABL.cc}

\subsection{Maximum flow}

\textbf{Max-flow min-cut theorem.} The maximum value of an $s$-$t$ flow is
equal to the minimum capacity over all $s$-$t$ cuts

\lst{Edges for flow algorithms}{graphs/flowedge.cc}
\underline{Runtime:} $\mathcal{O}(\lvert V \rvert \lvert E \rvert^2)$
\lst{Edmonds Karp}{graphs/edmondsKarp.cc}

\underline{Runtime:} $\mathcal{O}(\left| V \right|^3)$
\lst{Push Relabel}{graphs/pushRelabel.cc}

\underline{Runtime:} $\mathcal{O}(|V|^2|E|)$ For unit networks: $\mathcal{O}(|E|\sqrt{|V|})$
\lst{Dinic}{graphs/dinic.cc}

\subsubsection{Minimum s-t cut}

To find a minimal $s$-$t$ cut find all nodes that are reachable in the
residual network for a network w/ maximum flow from $s$.  This is the
$s$ part of the cut.  All other nodes belong to the $t$ part.

\subsubsection{Closure Problem}

A closure of a directed graph is a set of vertices with no outgoing
edges.  The closure problem is the task to find the maximum weighted
closure.  Solvable through reduction to a maximum flow problem: Add
source and target, connect all the vertices with positive weight $w$
to the source with capacity $w$ and connect all the vertices with
negative weight $w$ to the target with capacity $-w$.  All of the
edges in the original graph have infinite capacity in the new
graph.  The weight of the maximum weighted closure is equal to the sum
of all positive weighted vertices in the original graph minus the
maximum flow in the constructed graph.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
